\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{palatino}

\definecolor{darkmaroon}{RGB}{80, 0, 0}

\input{glyphtounicode}

\addtolength{\oddsidemargin}{-0.75cm}
\addtolength{\evensidemargin}{-0.75cm}
\addtolength{\textwidth}{1.5cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{2cm}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0cm}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\CVItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}
\newcommand{\CVSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\CVSubHeadingListStart}{\begin{itemize}[leftmargin=0.5cm, label={}]}
\newcommand{\CVSubHeadingListEnd}{\end{itemize}}

\newcommand{\PubSection}[1]{%
  \vspace{6pt}\noindent\textbf{#1}\vspace{3pt}%
}

%------------------------------------------------------------------------------
\begin{document}

%--HEADER----------------------------------------------------------------------
\begin{minipage}[t]{\textwidth}
  {\LARGE\textbf{\scshape Zilinghan Li}} \\[2pt]
  \textit{Machine Learning Engineer} \\[8pt]
  \normalsize
  Argonne National Laboratory \\
  Data Science and Learning Division \\
  9700 South Cass Ave, Building 240 \\
  Lemont, IL 60439-4844 \\
  Tel: 447-902-1841 \\
  {Email}: \href{mailto:zilinghan.li@anl.gov}{{zilinghan.li@anl.gov}}
\end{minipage}

\vspace{8pt}
\noindent{\color{darkmaroon}\rule{\linewidth}{2pt}}

\begin{center}
  {\Large\textbf{\scshape Curriculum Vitae}} \\[2pt]
  (05/17/2026)
\end{center}
\vspace{-4pt}

%--DEGREES---------------------------------------------------------------------
\section{Degrees Attained}
\begin{itemize}[leftmargin=1cm, label={}, itemsep=1pt]
  \small
  \item M.S., Computer Science, University of Illinois at Urbana-Champaign, May 2024 \hfill GPA: 4.0/4.0
  \item B.S., Computer Engineering, University of Illinois at Urbana-Champaign, May 2022 \hfill GPA: 3.89/4.0
  \item B.E., Computer Engineering, Zhejiang University, June 2022 \hfill GPA: 3.97/4.0
\end{itemize}

%--POSITIONS HELD--------------------------------------------------------------
\section{Professional Experience}
\CVSubHeadingListStart

\CVSubheading
{Argonne National Laboratory -- Data Science and Learning Division}{Lemont, IL}
{\textit{Machine Learning Engineer}}{May 2024 -- Present}
\begin{itemize}[leftmargin=0.5cm, label={$\bullet$}, topsep=2pt, itemsep=0pt]
  \small
  \item Led research and development of the APPFL federated learning framework, enabling privacy-preserving AI model training for biomedicine and general science. Authored 5 first-author and 1 co-first-author papers, with 20+ total manuscripts published or accepted at top-tier AI, computing, and biomedical venues.
  \item Developed AI solutions for biomedicine: automated pipelines for rare genetic disease screening, foundation models for digital histopathology image analysis, and multi-ancestry polygenic risk prediction tools.
  \item Contributed to evaluation and post-pretraining of large language models as part of the AuroraGPT project on DOE supercomputing resources.
  \item Contributing to the Transformational AI Models Consortium (ModCon), an Argonne-led DOE multi-laboratory consortium for building advanced scientific AI models, as part of the self-improving model team within the Baseline AI Capabilities (BASE) working group.
  \item Designed cost-effective algorithms for distributed computing across cloud and DOE HPC platforms, reducing operational costs by more than 70\%.
\end{itemize}

\vspace{-18pt}
\CVSubheading
{{}}{{}}
{\textit{Graduate Visiting Student}}{January 2023 -- May 2024}
\begin{itemize}[leftmargin=0.5cm, label={$\bullet$}, topsep=2pt, itemsep=0pt]
  \small
  \item Led development of APPFLx, a platform providing privacy-preserving cross-silo federated learning as a service for domain scientists across institutions. \href{https://appflx.link/}{\textbf{[Website]}}
\end{itemize}

\CVSubheading
{Amazon Web Services}{Sunnyvale, CA}
{\textit{Software Development Engineer Intern}}{May 2023 -- August 2023}
\begin{itemize}[leftmargin=0.5cm, label={$\bullet$}, topsep=2pt, itemsep=0pt]
  \small
  \item Developed a mobile application (Android/iOS) demonstrating the AWS IoT Device Location API for resolving device locations without built-in GPS.
\end{itemize}

\CVSubHeadingListEnd
\vspace{-6pt}

%--PUBLICATIONS, PRESENTATIONS, AND OTHER EVIDENCE----------------------------
\section{Publications, Presentations, and Other Evidence of Achievement}

\noindent\small\textit{Note: \textbf{Li, Z.} denotes the author. $^*$~denotes equal contribution. Lists are chronological, most recent first.}

%-- (3) Refereed Conference Proceedings ---------------------------------------
\PubSection{Publications in Refereed Conference and Workshop Proceedings}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small

  \item Li, Y., Dey, E., \textbf{Li, Z.}, Raghavan, K., Madduri, R., Kim, K. (2026). FedQueue: Queue-Aware Federated Learning for Cross-Facility HPC Training. In \textit{Proceedings of the 43rd International Conference on Machine Learning (ICML 2026)}. \href{https://arxiv.org/abs/2605.02125}{[arXiv]}

  \item Belagali, V., Kapse, S., Marza, P., Das, S., \textbf{Li, Z.}, Nandi, T., Madduri, R., Saltz, J., Christodoulidis, S., Vakalopoulou, M., Samaras, D. (2026). TICON: A Slide-Level Tile Contextualizer for Histopathology Representation Learning. In \textit{Findings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR Findings 2026)}. \href{https://arxiv.org/abs/2512.21331}{[arXiv]}



  \item Belagali, V., Yellapragada, S., Graikos, A., Kapse, S., \textbf{Li, Z.}, et al.\ (2026). Gen-SIS: Generative Self-augmentation Improves Self-supervised Learning. In \textit{Proceedings of the DataCV Workshop at the IEEE/CVF Conference on Computer Vision and Pattern Recognition (DataCV@CVPR 2026)}. \href{https://arxiv.org/abs/2412.01672}{[arXiv]}

  \item \textbf{Li, Z.}, He, S., Yang, Z., Ryu, M., Kim, K., Madduri, R., et al.\ (2025). Advances in APPFL: A Comprehensive and Extensible Federated Learning Framework. In \textit{Proceedings of the 25th IEEE International Symposium on Cluster, Cloud and Internet Computing (CCGrid 2025)}. \href{https://arxiv.org/abs/2409.11585}{[DOI]}

  \item Bai, G., Li, Y., \textbf{Li, Z.}, Zhao, L., Kim, K. (2025). FedSpaLLM: Federated Pruning of Large Language Models. In \textit{Proceedings of the 2025 Annual Conference of the Nations of the Americas Chapter of the ACL (NAACL 2025)}. \href{https://arxiv.org/abs/2410.14852}{[DOI]}

  \item Yellapragada, S., Graikos, A., Triaridis, K., \textbf{Li, Z.}, Nandi, T., Madduri, R., et al.\ (2025). Pathology Image Compression with Pre-trained Autoencoders. In \textit{Proceedings of the 28th International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI 2025)}. \href{https://arxiv.org/abs/2503.11591}{[DOI]}

  \item \textbf{Li, Z.}, Sinha, A., Li, Y., Chard, K., Kim, K., Madduri, R. (2025). Experiences Building Enterprise-Level Privacy-Preserving Federated Learning to Power AI for Science. In \textit{Proceedings of the 7th IEEE International Conference on Trust, Privacy and Security in Intelligent Systems, and Applications (TPS-ISA 2025)}. \href{https://arxiv.org/abs/2511.08998}{[arXiv]}

  \item Hiniduma, K., \textbf{Li, Z.}, Sinha, A., Madduri, R., Byna, S. (2025). CADRE: Customizable Assurance of Data Readiness in Privacy-Preserving Federated Learning. In \textit{Proceedings of the 21st IEEE International Conference on eScience (eScience 2025)}, pp.\ 121--130. \href{https://doi.org/10.1109/eScience65000.2025.00023}{[DOI]}

  \item Sinha, A., \textbf{Li, Z.}, Liu, T., Kindratenko, V., Kim, K., Madduri, R. (2025). Cost-Aware Federated Learning on the Cloud (Poster). In \textit{Proceedings of the 21st IEEE International Conference on eScience (eScience 2025)}, pp.\ 321--322. \href{https://arxiv.org/abs/2505.21727}{[DOI]}

  \item Sinha, A., \textbf{Li, Z.}, Liu, T., Kindratenko, V., Kim, K., Madduri, R. (2025). FedCostAware: Enabling Cost-Aware Federated Learning on the Cloud. In \textit{Proceedings of the 63rd Annual Allerton Conference on Communication, Control, and Computing (Allerton 2025)}. \href{https://arxiv.org/abs/2505.21727}{[arXiv]}


  \item \textbf{Li, Z.}, Chaturvedi, P., He, S., Chen, H., Singh, G., Kindratenko, V., Huerta, E.A., et al.\ (2024). FedCompass: Efficient Cross-Silo Federated Learning on Heterogeneous Client Devices Using a Computing Power Aware Scheduler. In \textit{Proceedings of the 12th International Conference on Learning Representations (ICLR 2024)}. \href{https://openreview.net/forum?id=msXxrttLOi}{[DOI]}

  \item Wilkins, G., Di, S., Calhoun, J., \textbf{Li, Z.}, Kim, K., Underwood, R., Mortier, R., et al.\ (2024). FedSZ: Leveraging Error-Bounded Lossy Compression for Federated Learning Communications. In \textit{Proceedings of the 44th IEEE International Conference on Distributed Computing Systems (ICDCS 2024)}. \href{https://arxiv.org/abs/2312.13461}{[DOI]}

  \item Madduri, R., \textbf{Li, Z.}, Nandi, T., Kim, K., Ryu, M., Rodriguez, A. (2024). Advances in Privacy Preserving Federated Learning to Realize a Truly Learning Healthcare System. In \textit{Proceedings of the 6th IEEE International Conference on Trust, Privacy and Security in Intelligent Systems, and Applications (TPS-ISA 2024)}. \href{https://arxiv.org/abs/2409.19756}{[DOI]}

  \item \textbf{Li, Z.}, He, S., Chaturvedi, P., Hoang, T.H., Ryu, M., Huerta, E.A., Kindratenko, V., Kim, K., Madduri, R. (2023). APPFLx: Providing Privacy-Preserving Cross-Silo Federated Learning as a Service. In \textit{Proceedings of the 19th IEEE International Conference on e-Science (e-Science 2023)}. \href{https://arxiv.org/abs/2308.08786}{[DOI]}

  \item Wu, Y., Miao, X., \textbf{Li, Z.}, He, S., Yuan, X., Yin, J. (2023). An Efficient Generative Data Imputation Toolbox with Adversarial Learning. In \textit{Proceedings of the 39th IEEE International Conference on Data Engineering (ICDE 2023)}. \href{https://ieeexplore.ieee.org/abstract/document/10184711}{[DOI]}

  \item Yuan, X.$^*$, \textbf{Li, Z.$^*$}, Wang, G. (2022). ActiveMatch: End-to-End Semi-Supervised Active Representation Learning. In \textit{Proceedings of the 2022 IEEE International Conference on Image Processing (ICIP 2022)}. \href{https://arxiv.org/abs/2110.02521}{[DOI]}

  \item \textbf{Li, Z.}, He, S., Du, Y., Gonz\'{a}lez, S., Schewe, K.D. (2021). Unbounded Barrier-Synchronized Concurrent ASMs for Effective MapReduce Processing on Streams. In \textit{Proceedings of the International Conference on Rigorous State-Based Methods (ABZ 2021)}. \href{https://doi.org/10.1007/978-3-030-77543-8_1}{[DOI]}
\end{enumerate}

\vspace{-6pt}
%-- (2) Refereed Journal Articles ---------------------------------------------
\PubSection{Refereed Journal Articles and Book Chapters}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item Hoang, T.H., Fuhrman, J., Klarqvist, M., Li, M., Chaturvedi, P., \textbf{Li, Z.}, Kim, K., Ryu, M., et al.\ (2025). Enabling End-to-End Secure Federated Learning in Biomedical Research on Heterogeneous Computing Environments with APPFLx. \textit{Computational and Structural Biotechnology Journal}. \href{https://arxiv.org/abs/2312.08701}{[DOI]}

  \item Patel, P., Corsi, A., Huerta, E.A., Merfeld, K., Tiki, V., \textbf{Li, Z.}, Bicer, T., Chard, K., et al.\ (2025). Radio Afterglow Detection and AI-driven Response (RADAR): A Federated Framework for Gravitational-wave Event Follow-up. \textit{The Astrophysical Journal Supplement Series}, 280(2), 71. \href{https://doi.org/10.3847/1538-4365/adfbea}{[DOI]}

  \item \textbf{Li, Z.}, He, S., Chaturvedi, P., Kindratenko, V., Huerta, E.A., Kim, K., Madduri, R. (2024). Secure Federated Learning Across Heterogeneous Cloud and High-Performance Computing Resources: A Case Study on Federated Fine-tuning of LLaMA 2. \textit{Computing in Science \& Engineering (CiSE)}. \href{https://arxiv.org/abs/2402.12271}{[DOI]}

  \item \textbf{Li, Z.}, Wang, X., Zhang, Z., Kindratenko, V. (2023). ViCTer: A Semi-Supervised Video Character Tracker. \textit{Machine Learning with Applications}. \href{https://doi.org/10.1016/j.mlwa.2023.100460}{[DOI]}
\end{enumerate}

%-- (5) Other Publications (Preprints) ----------------------------------------
\PubSection{Other Publications (Preprints and Manuscripts Under Review)}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item Li, Y., \textbf{Li, Z.}, Chard, K., Foster, I., Munson, T., Madduri, R., Kim, K. (2026). Scalable Cross-Facility Federated Learning for Scientific Foundation Models on Multiple Supercomputers. \textit{arXiv:2603.19544}. \href{https://arxiv.org/abs/2603.19544}{[arXiv]}

  \item Belagali, V., Marza, P., Yellapragada, S., \textbf{Li, Z.}, Nandi, T., Madduri, R., Saltz, J., Christodoulidis, S., Vakalopoulou, M., Samaras, D. (2025). CDG-MAE: Learning Correspondences from Diffusion Generated Views. \textit{arXiv:2506.18164}. Under review at \textit{Transactions on Machine Learning Research (TMLR)}. \href{https://arxiv.org/abs/2506.18164}{[arXiv]}


  \item Singhal, P.$^*$, \textbf{Li, Z.$^*$}, Yang, Z.$^*$, Nandi, T., Morse, C., Rodriguez, Z., Rodriguez, A., Kindratenko, V., Sirugo, G., Pyeritz, R.E., et al.\ (2025). Leveraging Open-Source Large Language Models to Identify Undiagnosed Patients with Rare Genetic Aortopathies. \textit{medRxiv}. Under review at \textit{Cell Med}.

  \item Yellapragada, S., Graikos, A., \textbf{Li, Z.}, Triaridis, K., Belagali, V., Kapse, S., et al.\ (2025). PixCell: A Generative Foundation Model for Digital Histopathology Images. \textit{arXiv:2506.05127}. Under review at \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence (TPAMI)}. \href{https://arxiv.org/abs/2506.05127}{[arXiv]}

  \item Levin, M.G., Koyama, S., Woerner, J., Zhang, D.Y., Rodriguez, A., Nandi, T., Truong, B., \textbf{Li, Z.}, et al.\ (2025). Genome-Wide Assessment of Pleiotropy Across $>$1000 Traits from Global Biobanks. \textit{medRxiv:2025.04.18.25326074}. Under review at \textit{Nature}. \href{https://www.medrxiv.org/content/10.1101/2025.04.18.25326074v2}{[medRxiv]}

  \item Cappello, F., Madireddy, S., Underwood, R., Getty, N., Chia, N.L.P., \textbf{Li, Z.}, et al.\ (2025). EAIRA: Establishing a Methodology for Evaluating AI Models as Scientific Research Assistants. \textit{arXiv:2502.20309}. Under review at \textit{International Journal of High Performance Computing Applications (IJHPCA)}. \href{https://arxiv.org/abs/2502.20309}{[arXiv]}
\end{enumerate}

%-- (13) Significant Software -------------------------------------------------
\PubSection{Significant Software Developed}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item \textbf{APPFL: Advanced Privacy-Preserving Federated Learning Framework} (\href{https://github.com/APPFL/APPFL}{github.com/APPFL/APPFL}). Led end-to-end design, development, and maintenance of this open-source federated learning framework. Metrics as of May 2026: 176 GitHub stars, 35 forks, Discord community of 67 users. Adopted and actively used by multiple U.S.\ DOE national laboratories, including Oak Ridge National Laboratory, Lawrence Berkeley National Laboratory, Sandia National Laboratories, and Los Alamos National Laboratory.
\end{enumerate}

%-- (6) Invited Talks ---------------------------------------------------------
\PubSection{Invited Talks Presented at Major Conferences and Symposia}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item ``Leveraging Open-Source LLMs-Enabled Identification of Undiagnosed Patients with Rare Genetic Aortopathies.'' \textit{AMIA 2025 Informatics Summit}, Pittsburgh, PA, March 2025.

  \item ``When Federated Learning Meets FABRIC.'' \textit{FABRIC Tutorials}, December 2024.

  \item ``Federated Learning Tutorial: Concepts, Challenges, and Framework.'' \textit{SciFM Summer School}, Ann Arbor, MI, July 2024.
\end{enumerate}

%-- (7) Seminars and Colloquia ------------------------------------------------
\PubSection{Seminars and Colloquia Presented}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item ``A Year in APPFL Software Development.'' \textit{AI4Science Quarterly Meeting}, Argonne National Laboratory, Lemont, IL, February 2025.

  \item ``APPFL Framework and Its Integration with MONAI.'' \textit{MONAI Federated Learning Working Group} (Virtual), February 2025.
\end{enumerate}

%-- (8) Other Presentations ---------------------------------------------------
\PubSection{Other Presentations and Contributed Talks}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item ``Advances in Privacy-Preserving Federated Learning to Realize a Truly Learning Healthcare System.'' \textit{TPS-ISA 2024}, Washington, D.C., October 2024.

  \item ``Using Globus Compute to Streamline Federated Learning Applications.'' \textit{ParslFest 2024}, Chicago, IL, October 2024.

  \item ``APPFLx.Link: Providing Privacy-Preserving Cross-Silo Federated Learning as a Service.'' \textit{ParslFest 2023}, Chicago, IL, October 2023.
\end{enumerate}

%-- (10) Leadership -----------------------------------------------------------
\PubSection{Leadership Provided to Scientific/Engineering/Technical Organizations}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item Technical lead and lead developer of the APPFL (Advanced Privacy-Preserving Federated Learning) open-source framework at Argonne National Laboratory, providing technical direction for the framework's architecture, development roadmap, and community engagement.
\end{enumerate}



%-- Graduate Students ---------------------------------------------------------
\PubSection{Graduate Students Mentored (Research Mentor)}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item \textbf{Ze Yang}, M.S.\ in Computer Science, University of Illinois at Urbana-Champaign (graduated; currently at Meta). Co-author, ``Advances in APPFL'' (CCGrid 2025).

  \item \textbf{Aditya Sinha}, M.S.\ in Computer Science, University of Illinois at Urbana-Champaign (graduated; currently at Microsoft). Lead author, ``FedCostAware'' (Allerton 2025) and ``Cost-Aware Federated Learning on the Cloud'' (eScience 2025).

  \item \textbf{Kaveen Hiniduma}, Ph.D.\ in Computer Science, Ohio State University (in progress). Lead author, ``CADRE'' (eScience 2025, pp.\ 121--130).

  \item \textbf{Rishi Kesav Mohan}, M.S.\ in Computer Science, University of Illinois at Urbana-Champaign (graduated; currently at Snowflake).

  \item \textbf{Abhijit Chunduru}, M.S.\ in Computer Science, University of Massachusetts Amherst (in progress).
\end{enumerate}

%-- (14) Major Projects -------------------------------------------------------
\PubSection{Major Projects Managed or Directed}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item \textbf{APPFL Framework Development (DOE-funded)}: Led technical direction and development of the APPFL framework at Argonne National Laboratory, coordinating contributions from partner national laboratories and external collaborators. Responsibilities include architecture design, feature development, testing, documentation, and integration with DOE computing infrastructure.
\end{enumerate}

%-- (16) Sustained Interaction ------------------------------------------------
\PubSection{Sustained Interaction with Sponsors}
\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item \textbf{U.S.\ Department of Energy (DOE)}: Ongoing technical contributor to DOE-funded research in privacy-preserving federated learning, distributed AI, and scientific computing, supporting DOE's mission to advance AI capabilities across national laboratories.
\end{enumerate}

\vspace{8pt}

%--PROFESSIONAL ACTIVITIES-----------------------------------------------------
\section{Professional Activities}
\begin{itemize}[leftmargin=1cm, label={$\bullet$}, itemsep=2pt]
  \small
  \item \textbf{Peer Reviewer} for the following journals and conferences (ordered by impact): CVPR, ICCV, ECCV, IEEE Transactions on Circuits and Systems for Video Technology (TCSVT), Journal of Medical Systems, Medical Physics, SoftwareX, Journal of Supercomputing, ETRI Journal, Journal of Digital Health, International Journal of Cloud Computing, NAACL Workshops
\end{itemize}

%--CITATION RECORD-------------------------------------------------------------
\section{Citation Record}

\noindent\small\textit{Source: Google Scholar (\href{https://scholar.google.com/citations?user=4JbL29YAAAAJ}{profile}), as of May 2026. \quad Total citations: \textbf{254} \quad h-index: \textbf{10} \quad i10-index: \textbf{10}}
\vspace{4pt}

\begin{enumerate}[leftmargin=1cm, label={[\arabic*]}, itemsep=3pt]
  \small
  \item \textbf{Li, Z.} et al.\ ``Advances in APPFL: A Comprehensive and Extensible Federated Learning Framework.'' \textit{CCGrid 2025.} \hfill\textbf{Cited by 45}

  \item \textbf{Li, Z.} et al.\ ``FedCompass: Efficient Cross-Silo Federated Learning on Heterogeneous Client Devices Using a Computing Power Aware Scheduler.'' \textit{ICLR 2024.} \hfill\textbf{Cited by 31}

  \item \textbf{Li, Z.} et al.\ ``APPFLx: Providing Privacy-Preserving Cross-Silo Federated Learning as a Service.'' \textit{e-Science 2023.} \hfill\textbf{Cited by 27}

  \item Hoang, T.H., \ldots, \textbf{Li, Z.} et al.\ ``Enabling End-to-End Secure Federated Learning in Biomedical Research with APPFLx.'' \textit{CSBJ 2025.} \hfill\textbf{Cited by 20}

  \item Bai, G., Li, Y., \textbf{Li, Z.} et al.\ ``FedSpaLLM: Federated Pruning of Large Language Models.'' \textit{NAACL 2025.} \hfill\textbf{Cited by 19}

  \item Wilkins, G., \ldots, \textbf{Li, Z.} et al.\ ``FedSZ: Leveraging Error-Bounded Lossy Compression for Federated Learning Communications.'' \textit{ICDCS 2024.} \hfill\textbf{Cited by 18}

  \item Yuan, X.$^*$, \textbf{Li, Z.$^*$}, Wang, G. ``ActiveMatch: End-to-End Semi-Supervised Active Representation Learning.'' \textit{ICIP 2022.} \hfill\textbf{Cited by 13}

  \item Cappello, F., \ldots, \textbf{Li, Z.} et al.\ ``EAIRA: Establishing a Methodology for Evaluating AI Models as Scientific Research Assistants.'' \textit{arXiv 2025} (under review at \textit{IJHPCA}). \hfill\textbf{Cited by 11}

  \item Madduri, R., \textbf{Li, Z.} et al.\ ``Advances in Privacy Preserving Federated Learning to Realize a Truly Learning Healthcare System.'' \textit{TPS-ISA 2024.} \hfill\textbf{Cited by 10}

  \item \textbf{Li, Z.} et al.\ ``Secure Federated Learning Across Heterogeneous Cloud and HPC Resources: A Case Study on Federated Fine-tuning of LLaMA 2.'' \textit{CiSE 2024.} \hfill\textbf{Cited by 10}

  \item Belagali, V., Yellapragada, S., \ldots, \textbf{Li, Z.} et al.\ ``Gen-SIS: Generative Self-augmentation Improves Self-supervised Learning.'' \textit{DataCV@CVPR 2026.} \hfill\textbf{Cited by 9}

  \item Yellapragada, S., Graikos, A., \textbf{Li, Z.} et al.\ ``PixCell: A Generative Foundation Model for Digital Histopathology Images.'' \textit{arXiv 2025} (under review at \textit{TPAMI}). \hfill\textbf{Cited by 7}

  \item Wu, Y., Miao, X., \textbf{Li, Z.} et al.\ ``An Efficient Generative Data Imputation Toolbox with Adversarial Learning.'' \textit{ICDE 2023.} \hfill\textbf{Cited by 7}

  \item Levin, M.G., \ldots, \textbf{Li, Z.} et al.\ ``Genome-Wide Assessment of Pleiotropy Across $>$1000 Traits from Global Biobanks.'' \textit{medRxiv 2025} (under review at \textit{Nature}). \hfill\textbf{Cited by 6}

  \item Sinha, A., \textbf{Li, Z.} et al.\ ``Cost-Aware Federated Learning on the Cloud.'' \textit{eScience 2025.} \hfill\textbf{Cited by 3}

  \item Patel, P., \ldots, \textbf{Li, Z.} et al.\ ``RADAR: A Federated Framework for Gravitational-wave Event Follow-up.'' \textit{Astrophys.\ J.\ Suppl.\ Ser.\ 2025.} \hfill\textbf{Cited by 2}

  \item \textbf{Li, Z.}, Sinha, A. et al.\ ``Experiences Building Enterprise-Level Privacy-Preserving Federated Learning to Power AI for Science.'' \textit{TPS-ISA 2025.} \hfill\textbf{Cited by 2}

  \item Yellapragada, S., \ldots, \textbf{Li, Z.} et al.\ ``Pathology Image Compression with Pre-trained Autoencoders.'' \textit{MICCAI 2025.} \hfill\textbf{Cited by 2}

  \item Belagali, V., \ldots, \textbf{Li, Z.} et al.\ ``TICON: A Slide-Level Tile Contextualizer for Histopathology Representation Learning.'' \textit{CVPR Findings 2026.} \hfill\textbf{Cited by 2}

  \item \textbf{Li, Z.}, Wang, X., Zhang, Z., Kindratenko, V. ``ViCTer: A Semi-Supervised Video Character Tracker.'' \textit{Machine Learning with Applications 2023.} \hfill\textbf{Cited by 2}

  \item Hiniduma, K., \textbf{Li, Z.} et al.\ ``CADRE: Customizable Assurance of Data Readiness in Privacy-Preserving Federated Learning.'' \textit{eScience 2025,} pp.\ 121--130. \hfill\textbf{Cited by 0}

  \item \textbf{Li, Z.}, He, S., Du, Y., Gonz\'{a}lez, S., Schewe, K.D. ``Unbounded Barrier-Synchronized Concurrent ASMs for Effective MapReduce Processing on Streams.'' \textit{ABZ 2021.} \hfill\textbf{Cited by 0}

  \item Li, Y., Dey, E., \textbf{Li, Z.} et al.\ ``FedQueue: Queue-Aware Federated Learning for Cross-Facility HPC Training.'' \textit{ICML 2026.}

  \item Sinha, A., \textbf{Li, Z.} et al.\ ``FedCostAware: Enabling Cost-Aware Federated Learning on the Cloud.'' \textit{Allerton 2025.}

  \item Li, Y., \textbf{Li, Z.} et al.\ ``Scalable Cross-Facility Federated Learning for Scientific Foundation Models on Multiple Supercomputers.'' \textit{arXiv 2026.}

  \item Belagali, V., \ldots, \textbf{Li, Z.} et al.\ ``CDG-MAE: Learning Correspondences from Diffusion Generated Views.'' \textit{arXiv 2025} (under review at \textit{TMLR}).
\end{enumerate}

\end{document}
